APPM 3310 Project\\\Large{Static Analysis of Truss Systems}

### 2016-04-25 paper.tex
Add boundary condition and solution sections.

@@

@@

\nocite{*}
\printbibliography{}

>>>>

Eq.~(\ref{eq:master_stiffness_equation}) is singular because while the truss
is \emph{hopefully} self constrained at this point it is not constrained in
space.  This is because Eq.~(\ref{eq:master_stiffness_equation}) does not yet
take into acount the fact that $\mathbf{u}$ is under some restrictions due to
constraints on the physical truss.  For the purpose of this paper, and the
accompanying software \parencite{shannon2016}, constraints will be limited to
one of the principal ($xyz$) dimensions.  Therefore, some of the entries of
$\mathbf{u}$ are forced to be zero and in these locations the force is
unknown.  The normal way to handle this is to simply remove the associated
rows and columns from $\mathbf{f}$, $\mathbf{u}$, and $K$.  However, in a
software package this either requires special logic when implementing
Eq.~(\ref{eq:global_to_master}) or requires reallocating a new $K$ matrix
after the fact.

Therefore, in this paper the computer friendly method outlined in section
3.5.2 of \cite{felippa2004ch3} is used.  This method involves setting the
diagonals of $K$ that correspond to the constrained parts of $\mathbf{u}$ to 1
and the corresponding values in $\mathbf{f}$ to 0.  This forces those elements
of $\mathbf{u}$ to solve to 0 displacement.  This is a simple $O(n)$ operation
instead of the higher order delete of rows and columns.

@@

Finally, Eq.~(\ref{eq:master_stiffness_equation}) is non-singular and thus can
be solved by any number of methods.  The result is the column vector of
displacements $\mathbf{u}$.  This gives the displacements of each node and
therefore the displacement of the endpoints of each element.  This is enough
to plot the new layout of the truss under load.

@@

% \nocite{*}
\printbibliography{}
